### 2021-10-26 SujetStage/2021-pNetsubjectM2.tex
sujet de stage

To tackle this issue, we ask: { \it Can we synthesise a global type from a collection of automata so as to ensure the composability of an open automaton  with compatible  surrounding automaton? }

@@

The main objective of the intern ship  deals with the characterization of interactions  of open automaton with its environment as behavioural types.
More specifically, the intern ship would follow the following steps:
\begin{itemize}
\item The internship will start with a familiarization with technical material: the semantics of  open automata and the notion behavioural types \cite{Hans:2016}, in particular the notion of session types that allows to describe the dynamic aspects of processes.

\item Design of an adequate characterisation of  compatibility condition  suitable for the composition open automata, and which is sufficient to decide if two open automata are compatible or not. 
\item Examples/Algorithm

>>>>

To tackle this issue, we ask: { \it Can we synthesise a global type from a collection of automata so as to ensure the composability of an open automaton  with a compatible  surrounding automaton? }

@@

The main objective of the internship is to deal with the characterization of interactions  of open automaton with its environment. These interactions can be characterised as behavioural types.
More specifically, the internship would follow the following steps:
\begin{itemize}
\item Familiarization with technical material: the semantics of  open automata and the notion behavioural types \cite{Hans:2016} that allows to describe the dynamic aspects of processes. In particular the notion of session types that focus on process interactions should be studied.

\item Design of an adequate characterisation of  compatibility condition  suitable for the composition open automata, and which is sufficient to decide if two open automata are compatible or not.

\item Application to the proof of absence of deadlock upon composition.

\item  We additionally have defined a notion of refinement between open automata that would benefit from such behavioural types. One additional objective of the internship could be to improve the definition of refinement based on the notion of behavioural types that has been defined in the previous steps.

\item Examples/Algorithm
